Supplementary Information: \nTree height, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2020-09-26 manuscript/response_to_reviews.Rmd

**We now report both marginal and conditional R2 in tables S8-S12**.

Other comments:

- As mentioned on a previous comment, in the manuscript the authors sampled dead and live trees, but then I did not see any further mentioning to this later in the manuscript (lines 175-178 and Table 2). This would merit some discussion and further analysis, how many trees were died and how many trees were alive of those in Table 2?

**We consider it extremely unlikely that the status at coring would affect drought response, particularly given the high resilience observed in the most recent round of analysis, and addressing this in the manuscript would add complexity and length not afforded by the journal's length requirements. We have modified the text at (former) lines 175-178 to make this more clear: "It is unlikely that drought was a factor in the death of any of these trees, as monthly May-Aug $PDSI$ did not drop below -1.75 (near-normal) in these years or the three years prior (2013-2017). Moreover, the trees analyzed here lived at least 17-18 years past the most recent major drought (1999), whereas the meta-analysis of @trugman_tree_2018 indicates that >10-year lags in drought-attributed mortality are rare. Having found that trees cored dead displayed similar climate sensitivity to trees cored live [@helcoski_growing_2019], we pooled the samples for this analysis.."**

### 2020-09-26 manuscript/climate_sensitivity_SI.Rmd
Updated SI table and figure names
minor modification of appendix s1
rename methods s1, cut some text

**Appendix S1. Further Package Citations**

@@

![**Figure S6. Drought recovery, $Rc$, across species for the three focal droughts.**](tables_figures/publication/FigureS6_density_plot_recovery.png)

@@

\newpage
## Appendix S1. Further Package Citations
While there were several R-packages we used for a specific purpose in our methods, numerous packages were immensely helpful for this research behind the scenes. As in all of science, this study is a representation of the work done by both the authors of this paper as well as countless others. While acknowledging everyone is impossible, we want to at least give thanks to those who made this work possible.

R-packages not already cited in the main manuscript include the following, listed alphabetically by corresponding package name:

@@

>>>>

**Methods S1. Further Package Citations**

@@

![**Figure S6. Density plot of Recovery ($Rc$) values for each focal year.**](tables_figures/publication/FigureS6_density_plot_recovery.png)

@@

\newpage
## Methods S1. Further Package Citations
While there were several R-packages we used for a specific purpose in our methods, numerous packages were immensely helpful for this research behind the scenes. R-packages not already cited in the main manuscript include the following, listed alphabetically by corresponding package name:

@@

### References
